Trajectory model of passive kelp dispersal

### 2020-08-17 thesis_chapter_3.Rmd
update started

## Air-form drag

>>>>

The use of shape coefficients was used as a novel approach to simulating biological drifting debris. The drag coefficient for a spherical particle was used in the calculation of hydrodynamic drag as the trajectory model assumes the particles are spherical. The cross-sectional area for each of the virtual kelp parts was determined and used in the calculation of hydrodynamic drag.
